Plots for Latent Hawkes Paper

### 2020-07-26 output_scripts/Paper_Plots.Rmd
add some more plots for slides

@@

```{r prepare data for 4b}
plot.s <- 9
plot.i <- 4
plot.j <- 5

@@

# Figure 5:
```{r data for fig 5}
load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
load(paste(sim_data_path,"fit123_state_est.RData",sep=''))
## Initialize
N_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
Lambda_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
Lambda_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
Lambda_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
Lambda_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
PR_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
PR_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
PR_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
PR_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
KS_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_p_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_p_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_p_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_p_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))

@@

@@

matrix_lst_plot <- list(
                        indep_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                        m1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m3_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]]) 
#cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-60,max=60,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst=list("I-MMHP","C-HP","C-DCHP","DC C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-60,-30,0,30,60), fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,1)
                  )

```
<!-- The remaining plot code seems to mostly be in `PaperPlots.R`. -->

@@

temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
p3 <- ggplot(temp_plot_df, aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 50)
p3
```

@@

```{r fig-8b-frob-norm-all-cohorts}
load("../output/plot_N_predict.RData")
temp_plot_df <- all_cohort_norm_df %>% 
  group_by(day, method) %>% 
  summarize(avg=mean(norm), n= n(), sd=sd(norm))

@@

@@

# png(paste(plot_path,"real_predict_rank_all_cohort.png",sep=""),width=600,height=300)
p6 <- ggplot(temp_plot_df, aes(x=day, y=avg, group=method, color=method)) + 
  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
                position=position_dodge(0.2)) +
  scale_fill_manual(values = viridis::viridis(5)) +
  #scale_color_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) +
  ggtitle("(b)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 18)) +
  xlab("Prediction horizon (day)") + 
  ylab("Spearman rank correlation") + 
  coord_cartesian(ylim=c(0,1)) + 
  guides(color=guide_legend(title="Model")) 
p6
```

>>>>

```{r, eval=FALSE}
par(mar=c(3,3,1,1))
plot(as.vector(n_matrix[n_matrix>0]), as.vector(ks.stat.matrix[n_matrix>0]),
     xlab="", ylab="", pch=16, col="gray", cex= 0.8, xaxt="n", yaxt="n",
     ylim=c(0,0.65))
mtext("Number of events", cex=1.5, side=1, line=1.8)
mtext("K-S statistics", cex=1.5, side=2, line=1.5)
mgp.axis(1,mgp=c(0,0.3,0),at=seq(0,120,10),cex.axis=1,lwd=0,lwd.ticks=0.1)
mgp.axis(2,mgp=c(0,0.1,0),at=seq(-0.2,0.6,0.2),cex.axis=1,lwd=0,lwd.ticks=0.8)
```

@@

```{r prepare data for 4b,cache=TRUE}
plot.s <- 9
plot.i <- 4
plot.j <- 5

@@

# Figure 5:
```{r data for fig 5,cache=TRUE}
load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
load(paste(sim_data_path,"fit123_state_est.RData",sep=''))
## Initialize
N_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
Lambda_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
Lambda_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
Lambda_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
Lambda_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
PR_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
PR_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
PR_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
PR_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1))) 
KS_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_p_model1_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_p_model2_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_p_model3_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))
KS_p_true_array <- array(0,dim=c(n_sim,length(object_par$f_vec_1),length(object_par$f_vec_1)))

@@

```{r fig-rank-slides, fig.height=3}

p2_slides <- plot_cor_df %>%
  filter(Method != "Agg-rank") %>%      
  ggplot(aes(x="", y = cor, fill = Method)) +
        geom_boxplot(alpha=0.7, width=0.5) +
        scale_fill_manual(values = viridis::viridis(3)) + 
        #ggtitle("(b)") +
        ylim(0,1) +
        theme_bw() +
        theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
              text = element_text(size = 20),
              axis.text.y =element_text(size = 11),
              legend.position="none",
              axis.title.x=element_blank()) +
        facet_grid(cols=vars(Method)) +
        ylab("Rank correlation")
p2_slides

@@

matrix_lst_plot <- list(
                        indep_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                        m1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m3_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]]) 
#cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-80,max=80,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-80,-40,0,40,80), fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,1)
                  )

```{r fig_pr_slides, fig.height=3, fig.width=7}
current_cohort <- 5

matrix_lst_plot <- list(
                        #indep_pr[rev(expert_rank_10[[current_cohort]]),
#                                                                   #expert_rank_10[[current_cohort]]],
                        m1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                  expert_rank_10[[current_cohort]]],
                        m2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m3_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]]) 
#cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=3,n_row=1,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-80,max=80,axis_cex=1,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst=list("C-HP","C-DCHP","C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-80,-40,0,40,80), fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,0.5)
                  )

<!-- The remaining plot code seems to mostly be in `PaperPlots.R`. -->

@@

temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
p3 <- temp_plot_df %>%
  rowwise() %>%
  mutate(norm = min(norm,60)) %>%
  ggplot( aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 60)
p3
```

@@

```{r fig-8b-frob-norm-all-cohorts}
load("../output/plot_N_predict.RData")
temp_plot_df <- all_cohort_norm_df %>% 
  group_by(day, method) %>% 
  summarise(avg=mean(norm), n= n(), sd=sd(norm))

@@

```{r fig-slides-predict}
load("../output/plot_N_predict_new.RData")
temp_plot_df <- all_cohort_norm_df %>% 
  group_by(day, method) %>% 
  summarise(avg=mean(norm), n= n(), sd=sd(norm),
            se = sd/sqrt(n))

#png(paste(plot_path,"real_predict_N_all_cohort.png",sep=""),width=600,height=300)
p4_slides <- ggplot(temp_plot_df, 
                    aes(x=day, y=avg, group=method, color=method)) + 
  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
                 position=position_dodge(0.2)) +
  scale_color_manual(values = viridis::viridis(5)) + 
  #ggtitle("(b)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 18)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") + 
  coord_cartesian(ylim=c(2.5,57.5)) + 
  guides(color=guide_legend(title="Model")) 
p4_slides

```{r}

all_sims <- do.call(rbind,predict_day_norm_df_lst)

temp_plot_df <- all_sims %>% 
  group_by(day, method) %>% 
  summarise(avg=mean(norm), n= n(), sd=sd(norm),
            se = sd/n)

temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
p4_slides <- temp_plot_df %>% #filter(method != "C-HP") %>% 
  #filter(method != "I-MMHP") %>%
  ggplot(aes(x=day, y=avg, group=method, color=method)) + 
  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
                 position=position_dodge(0.2)) +
  scale_color_manual(values = viridis::viridis(5)) + 
  #ggtitle("(b)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 18)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") + 
  coord_cartesian(ylim=c(2.5,57.5)) + 
  guides(color=guide_legend(title="Model")) #+ ylim(c(0,1000))
p4_slides

@@

# png(paste(plot_path,"real_predict_rank_all_cohort.png",sep=""),width=600,height=300)
p6 <- ggplot(temp_plot_df, aes(x=day, y=avg, group=method, color=method)) + 
  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
                position=position_dodge(0.2)) +
  scale_color_manual(values = viridis::viridis(5)) +
  #scale_color_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) +
  ggtitle("(b)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 18)) +
  xlab("Prediction horizon (day)") + 
  ylab("Spearman rank correlation") + 
  coord_cartesian(ylim=c(0,1)) + 
  guides(color=guide_legend(title="Model")) 
p6
```
